Drought indices of water demand and supply, soil moisture, vegetation, and its impact on LULCC in continental Chile

### 2024-01-17 article/paper_drought_Chile2023.tex
actualizar repo oficina GEMA

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, boxrule=0pt, enhanced, sharp corners, interior hidden]}{\end{tcolorbox}}\fi

>>>>

\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[breakable, borderline west={3pt}{0pt}{shadecolor}, frame hidden, boxrule=0pt, interior hidden, sharp corners, enhanced]}{\end{tcolorbox}}\fi
